Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-18 ieee_paper.tex
harmonizing width
captions

%  \includegraphics[width=\linewidth]{figures/matrix_not.pdf}
  \caption{Matrix of the computation.}
  \label{fig:mat_struct}
\end{figure}

@@

  \caption{On MIC with 240 threads, 64-byte memory
    alignment. Bandwidth performance under idealized
    conditions as a function of matrix row size.  Entries with "cpp"
    denote cases where coding was performed without MIC vector
    instructions. \todo{legend} }
  \label{fig:bandwidth}
  \label{fig:band_rw_MIC}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/bandwidth_gather_unpack.pdf}
  \caption{Performance of gather and unpack operations.}
  \label{fig:band_gather} 
\end{figure}
%

@@

\begin{figure*}[t]
  \centering
  \subfigure[Supercompact and Random.]{\includegraphics[width=.48\linewidth]{figures/random_supercompact.pdf}\label{fig:perf_ideal}}
  \subfigure[Compact and RBF-FD.]{\includegraphics[width=.48\linewidth]{figures/rbf_compact.pdf}\label{fig:perf_realistic}}

@@

  \caption{Performance of $y=Ax$ on the MIC. Squares:
    base 1/1 case, solid circles: 4/4 case implemented in C++, solid
    triangles: 4/4 case implemented with MIC vector instructions. Each
    symbol has two cases: with (red) and without (blue) Reverse
    Cuthill-McKee bandwidth reduction. The grid is $96^3$. Vectorization matters in practice. Differences in BW
    translate in different performance.\todo{legend} \todo{fix caption}}
  \label{fig:comparison_spmv}
  \label{fig:perf_mic}
\end{figure}

>>>>

  \caption{Matrix of the computation.}
  \label{fig:mat_struct}
\end{figure}

@@

  \caption{Bandwidth performance under idealized conditions.  Entries
    with "cpp" (triangles) denote cases where vectorization is
    compiler generated. \todo{legend} }
  \label{fig:bandwidth}
  \label{fig:band_rw_MIC}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=.9\linewidth]{figures/bandwidth_gather_unpack.pdf}
  \caption{Performance of gather and unpack operations.}
  \label{fig:band_gather} 
\end{figure}
%

@@

\begin{figure*}[t]
  \centering
  \subfigure[Supercompact and Random.]{\includegraphics[width=.45\linewidth]{figures/random_supercompact.pdf}\label{fig:perf_ideal}}
  \subfigure[Compact and RBF-FD.]{\includegraphics[width=.45\linewidth]{figures/rbf_compact.pdf}\label{fig:perf_realistic}}

@@

  \caption{Performance of $y=Ax$ for a RBF derivative stencil of a
    $96^3$ 3D grid. Classical SpMV ($n_m=n_v=1$ given in blue) has low
    performance. The manually vectorized code (red) is 3.5 times
    faster than the compiler generated one (green). RCM ordering
    (squares) only improves the performance for our manually
    vectorized code.}
  \label{fig:comparison_spmv}
  \label{fig:perf_mic}
\end{figure}
